\bibitem{bmodes}
Guzzetti, M.C.; Bartolo, N.; Liguori, M.; Martarrese, S. (2016). Gravitational waves from inflation. {\em arXiv:1605.01615v3}.

\bibitem{hobbs_dai}
Hobbs, George; Dai, Shi. (2017). A review of pulsar timing array gravitational wave research. {\em arXiv:1707.01615v1}

\bibitem{PriceTails}
Price, Richard H. (1972). Nonspherical Perturbations of Relativistic Gravitational Collapse. I Scalar and Gravitational Perturbations. {\em Phys. Rev. D} 5, 10. 
\bibitem{2ndOrderSource}
Miller, Jeremy; Wardell, Barry; Pound, Adam. (2016). Second-order perturbation theory: the problem of infinite mode coupling. {\em arXiv:1608.0783v1}.

\bibitem{AnnasThesis}
Heffernan, Anna. (2012). The Self-Force Problem: Local Behavior of the Detweiler-Witing Singular Field. University College Dublin. {\em arXiv:1403.6177v1}.

\bibitem{bertiKerrQNM}
Yang, Huan; Zimmerman, Aaron; Zenginoglu, Anil; Zhang, Fan; Berti, Emanuele; Chen, Yanbei. (2013). Quasinormal modes of nearly extremal Kerr spacetimes: spectrum bifurcation and power-law ringdown. {\em arXiv:1307.8086v1}.

\bibitem{bertiSchwQNM}
Berti, Emanuele; Cardoso, Vitor; Starinets, Andrei O. Quasinormal modes of black holes and black branes. {\em arXiv:0905.2975v2}

\bibitem{coordinateTransform}
Philipp, Dennis; Perlick, Volker. (2015). On analytic solutions of wave equations in regular coordinate systems on Schwarzchild background. {\em arXiv:1503.08101v1} 

\bibitem{Detweiler_messaritaki_whiting}
Diaz-Rivera, Luz Maria; Messaritaki, Eirini; Whiting, Bernard F.; Detweiler, Steven. (2004). Scalar field self-force effects on orbits about a Schwarzschild black hole. {\em arXiv:gr-qc/0410011v1}.

\bibitem{diener_vega_wardell_detwieler_2012}
Diener, Peter; Vega, Ian; Wardell, Barry; Detweiler, Steven. Self-consistent orbital evolution of a particle around a Schwarzschild black hole. {\em arXiv:1112.4821v3}.

\bibitem{dirac1938}
Dirac, P. A. M. (1938). Classical theory of radiating electrons. {\em Royal Society Publishing.}

\bibitem{eLISAastrophysicsSelfForce}
Amaro-Seoane, Pau; Gair, Jonathon R.; Pound, Adam; Hughes, Scott A.; Sopuerta, Carlos F. (2014). Research Update on Extreme-Mass-Ratio Inspirals. {\em arXiv:1410.0958v1}.

\bibitem{ELISAz}
Gair, Jonathan R.; Porter, Edward K. (2012). Observing extreme-mass-ratio inspirals with eLISA/NGO. {\em arXiv:1210.8066v1}

\bibitem{gralla_harte_wald_2009}
Gralla, Samuel E.; Harte, Abraham I.; Wald, Robert M. (2009). A Rigorous Derivation of Electromagnetic Self-force. {\em arXiv:0905.2391v2}.

\bibitem{heffernan_ottewil_wardell_modesum_basisForCode}
Heffernan, Anna; Ottewil, Adrian; Wardell, Barry; (2013). High-order expansions of the Detweiler-Whiting singular field in Schwarzschild spacetime. {\em arXiv:1204.0794v4}.

\bibitem{hyperboloidalCoordinates}
Bernuzzi, Sebastiano; Nagar, Alessandro; Zenginoglu, Anil. (2011). Binary black hole coalescence in the large-mass-ratio limit: the hyperboloidal layer method and waveforms at null infinity. {\em arXiv:1107.5402v2}.

\bibitem{LISA02062017}
Danzmann, Karsten. (2017). LISA Laser Interferometer Space Antenna: A proposal in response to the ESA call for L3 mission concepts. 

\bibitem{LISAscienceMarch28_2017}
Babak, Stanislav. (2017). Science with the space-based interferometer LISA. V: Extreme mass-ratio inspirals. {\em arXiv:1703.09722v1}.

\bibitem{miller_wardell_pound_ylm_2ndorder}
Miller, Jeremy; Wardell, Barry; Pound, Adam. (2016). Second-order perturbation theory: the problem of infinte mode coupling. {\em arXiv:1608.06783v1}.

\bibitem{minosasakitanaka}
Mino, Yasushi; Sasaki, Misao; Tanaka, Takahiro. (1996). Gravitational Radiation Reaction to a Particle Motion. {\em arXiv:gr-qc/9606018v1}.

\bibitem{OmegaTransferFunction}
Yunes, Nicolas; Wofgang, Tichy; Owen, Benjamin J.; Briigmann, Bernd. (2006). Binary black hole initial data from matched asymptotic expansions. {\em arXiv:gr-qc/0503011v3}.

\bibitem{poisson_pound_vega_living_review}
Poisson, Eric; Pound, Adam; Vega, Ian. (2011). The Motion of Point Particles in Curved Spacetime. {\em arXiv:1102.0529v3}.

\bibitem{pound2ndOrderSelfForce0}
Pound, Adam. (2012). Second-order gravitational self-force. {\em arXiv:1201.5089v2}.

\bibitem{pound2ndOrderSelfForce}
Pound, Adam. (2017). Nonlinear gravitational self-force: second-order equation of motion. {\em arXiv:1703.02836v1}.

\bibitem{pound_poisson}
Pound, Adam; Poisson, Eric. (2008). Osculating orbits in Schwarzschild spacetime, with an application to extreme mass-ratio inspirals. {\em Phys. Rev. D} 77, 044013.

\bibitem{quinn}
Quinn, Theodore, C. (2000). Axiomatic approach to radiation reaction of scalar point particles in curved spacetime. {\em arXiv:qr-qc/0005030v1}.

\bibitem{quinnwald}
Quinn, Theodore C.; Wald, Robert M. An Axiomatic approach to electromagnetic and gravitational radiation reaction of particles in curved spacetime. {\em arXiv:gr-qc/9610053v1}.

\bibitem{time_dependent_coordinate_transformation}
Field, Scott E.; Hesthaven, Jan S.; Lau, Stephen R. Discontinuous Galerkin method for computing gravitational waveforms from extreme mass ratio binaries. {\em arXiv:0902.1287v2}.

\bibitem{tukolsky_hyperboloidal}
Zenginoglu, Anil; Khanna, Gaurav. (2011). Null infinity waveforms from extreme-mass-ratio inspirals in Kerr spacetime. {\em arXiv:1108.1816v2}.

\bibitem{vega_diener_tichy_detweiler}
Vega, Ian; Diener, Peter; Tichy, Wolfgang; Detweiler, Steven. (2009). Self-force with (3+1) codes: a primer for numerical relativists. {\em arXiv:0908.2138v1}.

\bibitem{vega_wardell_diener_2011}
Vega, Ian; Wardell, Barry; Diener, Peter. (2011). Effective source approach to self-force calculations. {\em arXiv:1101.2925v1}.

\bibitem{Vega_wardell_diener_cupp_haas_2013}
Vega, Ian; Wardell, Barry; Diener, Peter; Cupp, Samuel; Haas, Roland. (2013). Scalar self-force for eccentric orbits around a Schwarzschild black hole. {\em arXiv:1307.3476v2}.

\bibitem{vega_wardel_diener_cupp_haas_accelcirc}
Vega, Ian; Wardell, Barry; Diener, Peter; Cupp, Samuel; Hass, Roland. (2013). Scalar self-force for eccentric orbits around a Schwarzschild black hole. {\em arXiv:1307.3476v2}.

\bibitem{WardellSelfForceReview}
Wardell, Barry. (2015). Self-Force: Computational Strategies. {\em arXiv:1501.07322v3}.

\bibitem{wardell_vega_thornburg_diener}
Wardell, Barry; Vega, Ian; Thornburg, Jonathan; Diener, Peter. (2012). Generic effective source for scalar self-force calculations. {\em arXiv:1112.6355v3}.



\bibitem{GW150914}
LIGO Virgo Collaboration. (2016). Observation of Gravitational Waves from a Binary Black Hole Merger. {\em Phys. Rev. Lett.} 116, 061102.

\bibitem{GW151226}
LIGO Virgo Collaboration. (2016). GW151226: Observation of Gravitational Waves from a 22-Solar-Mass Binary Black Hole Coalescence. {\em Phys. Rev. Lett} 116, 241103.
  
\bibitem{GW170104}
  LIGO Virgo Collaboration. (2017). GW120104: Observation of a 50-Solar-Mass Binary Black Hole Coalescence at Redshift 0.2. {\em Phys. Rev. Lett.} 118, 221101.

\bibitem{LIGO1a}
  LIGO Virgo Collaboration. (2016). Observing Gravitational-wave Transient GW150914 with Minimal Assumptions. {\em Phys. Rev. D} 93, 122004.

\bibitem{LIGO1b}
  LIGO Virgo Collaboration. (2016). GW150914: First Results from the Search for Binary Black Hole Coalescence with Advanced LIGO. {\em Phys. Rev. D} 93, 122003.
\bibitem{LIGO1c}
  LIGO Virgo Collaboration. (2016). The Rate of Binary Black Hole Mergers Inferred from Advanced LIGO Observations Surrounding GW150914. {\em Accepted Astrophys. J. Lett}

\bibitem{LIGO1d}
  LIGO Virgo Collaboration. (2016). Astrophysical Implications of the Binary Black-Hole Merger GW150914. {\em Astrophys. J. Lett} 818, L22.

\bibitem{LIGO1e}
  LIGO Virgo Collaboration. (2016). Tests of General Relativity with GW150914. {\em Phys. Rev. Lett.} 116, 221101.
  
\bibitem{LIGO1f}
  LIGO Virgo Collaboration. (2016). GW150914: Implications for the Stochastic Gravitational Wave Background from Binary Black Holes. {\em Phys. Rev. Lett.} 116, 131102.

\bibitem{LIGO1g}
  LIGO Virgo Collaboration. (2016). Calibration of the Advanced LIGO Detectors for the Discovery of the Binary Black-hole Merger GW150914. {\em Submitted to Phys. Rev. D}.

\bibitem{LIGO1h}
  LIGO Virgo Collaboration. (2016). Characterization of Transient Noise in Advanced LIGO Relevant to Gravitational Wave Signal GW150914. {\em Class. Quant. Grav.} 33, 134001.

\bibitem{LIGO1i}
  LIGO Virgo Collaboration and ANTARES and IceCube Collaborations. (2016). High-energy Neutrino Follow-up Search of Gravitational Wave Event GW150914 with ANTARES and IceCube. {\em Phys. Rev. D} 93 122010. 

\bibitem{LIGO1j}
  LIGO Virgo Collaboration. (2016). GW150914: The Advanced LIGO Detectors in the Era of First Discoveries. {\em Phys. Rev. Lett.} 116, 131103.

\bibitem{LIGO1k}
  LIGO Virgo, ASKAP, BOOTES, Dark Energy Survey and Camera, GW-EM, Fermi GBM and LAT, GRAWITA, INTEGRAL, IPTF, InterPlanetary, J-GEM, La Silla-Quest, Liverpool Telescope, LOFAR, MASTER, MAXI, MWA, PAN-STARRS, PESSTO, PI of the Sky, SkyMapper, Swift, TAROT, Zadko, Algerian National Observatory, C2PU, TOROS, and VISTA Collaborations. (2016). Localization and Broadband Follow-up of the Gravitational-wave Transient GW150914. {\em Astrophys. J. Lett.} 826, L13.
  
\bibitem{Bambi2017}
  Bambi, Cosimo. (2017) Testing black hole candidates with electromagnetic radiation. {\em Reviews of Modern Physics} 89.
\bibitem{LIGOsensitivity}
  Martynov, D.V., et al. (2016). Sensitivity of the Advanced LIGO detectors at the beginning of gravitational wave astronomy. {\em Phys. Rev. D} 93, 112004.
\bibitem{PoissonLivingReviews}
  Poisson, Eric; Pound, Adam; Vega, Ian. (2011). The motion of point particles in curved spacetime. {\em Living Reviews in Relativity}. 14, 7. 

\bibitem{dghesthaven}
 Hesthaven, Jan S.; Warburton, Tim. (2008). {\em Nodal Disconintuous Galerkin Methods: Algroithms, Analysis, and Applications.} Springer.

\bibitem{LIGOSaulson}
 Saulson, Peter R. (1994). {\em Fundamentals of Interferometric Gravitational Wave Detectors.} World Scientific Publishing Co.

\bibitem{NRinC++}
 Press, William H.; Teukolsky, Saul A.; Vetterling, William T.; Flannery, Brian P. (2002). {\em Numerical Recipes in C++: The Art of Scientific Computing.} The Press Syndicate of the University of Cambridge.

\bibitem{Mathematica}
 Wolfram, Stephen. (2016). {\em An Elementary Introduction to the Wolfram Language.} Wolfram-Media, inc.

\bibitem{Python}
 Newman, Mark. (2013). {\em Computational Physics.} University of Michigan.

\bibitem{Wald}
Wald, Robert M. (1984). {\em General Relativity.} The University of Chicago.

\bibitem{Carroll}
Carroll, Sean M. (2004). {\em An Introduction ot General Relativity Spacetime and Geometry.} Addison Wesley.

\bibitem{MTW}
Misner, Charles W.; Thorne, Kip S.; Wheeler, John Archibald. (1973). {\em Gravitation.} W. H. Freeeman and Company. 

