\documentclass[12pt,letterpaper]{lsuetd}
\usepackage{setspace,graphics,dsfont,verbatim,paralist,indentfirst}
\setlength{\topmargin}{-0.5in}
\setlength{\textheight}{9.0in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\textwidth}{1.00in}
\setlength{\parindent}{1.75em}
\setlength{\parskip}{0ex}
\setcounter{tocdepth}{2}

\makeatletter

\begin{document}
\renewcommand\@pnumwidth{1.55em}
\renewcommand\@tocrmarg{9.55em}
\renewcommand*\l@chapter{\@dottedtocline{0}{1.5em}{2.3em}}
\renewcommand*\l@figure{\@dottedtocline{1}{0em}{3.1em}}
\let\l@table\l@figure

\pagenumbering{roman}
\thispagestyle{empty}
\begin{center}
%The title page is first created.
  TOWARD GRAVITATIONAL WAVEFORMS FOR EXTREME AND INTERMEDIATE MASS RATIO INSPIRALS OF BLACK HOLE BINARY SYSTEMS: STRATEGIES FOR COMPUTING THE SELF-FORCE OF A SCALAR FIELD ON A SCHWARZSCHILD SPACETIME BACKGROUND DUE TO CAUSAL CONNECTIONS BETWEEN THE PARTICLE'S PAST ORBIT AND PRESENT POSITION USING THE DISCONTINUOUS GALERKIN, EFFECTIVE SOURCE, AND OSCULATING ORBIT METHODS

\vfill
\doublespacing
A Thesis/Dissertation \\
\singlespacing
Submitted to the Graduate Faculty of the \\
Louisiana State University and \\
Agricultural and Mechanical College \\
in partial fulfillment of the \\
requirements for the degree of \\
Master of Science\\
\doublespacing
in \\
                                       
Physics\\
\singlespacing
\vfill

by \\
Steven (Susan) Dorsher \\
B.S., Massachusetts Institute of Technology, 2004  \\
M.S., The Ohio State University, 2006  \\
M.S., University of Minnesota, 2013  \\
%If necessary, copy and paste the previous line here to include a master's degree.
December, 2017
\end{center}
\pagebreak
%The Copyright Page and Dedication sections can be added here, if desired.

%\chapter*{Copyright Page}
%\doublespacing
%\vspace{0.55ex}
%Insert the appropriate text for the copyright page here.
%\addcontentsline{toc}{chapter}{\hspace{-1.5em} {COPYRIGHT PAGE} \vspace{12pt}}
%\pagebreak

%\chapter*{Dedication}
%\doublespacing
%\vspace{0.55ex}
%Insert the appropriate text for the dedication or epigraph page here.  This part of the ETD must not exceed one page.
%\addcontentsline{toc}{chapter}{\hspace{-1.5em} {DEDICATION} \vspace{12pt}}
%\pagebreak

\chapter*{Acknowledgments}
\doublespacing
\vspace{0.55ex}
I would like to thank Peter Diener and Frank L\"{o}ffler for their guidance. Peter Diener especially has been very important to me, both as an advisor and personally. I would also like to thank Gabriela Gonzalez for the excellent opportunity to work on LIGO during the time of three detections, which provided me the funding I needed to continue the work detailed in this document. I would like to thank Juana Moreno for the opportunity to work as a stand in for her outreach coordinator to the LA-SIGMA Research Experience for Undergraduates and High School Students program my first summer at Louisiana State University, which also helped provide funding for this research. My parents, Paul and Joanne Dorsher, also deserve a mention, both for extraordinary moral support and for the financial support they provided that helped make this possible. I would also like to thank my sister, Patricia Dorsher, and my friends Hope Ring and Christy Paulson, for being there for me. And of course, I would like to thank my committee, Peter Diener (chair), Jorge Pullin (co-chair), Gabriela Gonzalez, Steven Brandt, and Juhan Frank. 

%The code below adds the Acknowledgments section to the Table of Contents.
\addcontentsline{toc}{chapter}{\hspace{-1.5em} {ACKNOWLEDGMENTS} \vspace{12pt}}
\pagebreak
%The Preface section can now be added, if desired.

%\chapter*{Preface}
%\doublespacing
%\vspace{0.55ex}
%Insert the appropriate text for the preface here.
%\addcontentsline{toc}{chapter}{\hspace{-1.5em} {PREFACE} \vspace{12pt}}
%\pagebreak

\singlespacing
\tableofcontents
\pagebreak

%The code below generates the List of Tables and adds it to the Table of Contents.
\renewcommand\@pnumwidth{1.55em}
\renewcommand\@tocrmarg{8.55em}
\addcontentsline{toc}{chapter}{\hspace{-1.5em} LIST OF TABLES \vspace{12pt}}
\listoftables
\pagebreak
%The code below generates the List of Figures and adds it to the Table of Contents.
\addcontentsline{toc}{chapter}{\hspace{-1.5em} LIST OF FIGURES \vspace{12pt}}
\listoffigures
\pagebreak
%The List of Nomenclature may be included here, if desired.

%\chapter*{List of Nomenclature}
%\doublespacing
%\vspace{0.55ex}
%Provide the definitions of the symbols used in your thesis or dissertation here.
%\addcontentsline{toc}{chapter}{\hspace{-1.5em} LIST OF NOMENCLATURE \vspace{12pt}}
%\pagebreak

%The code below adds the Abstract and places it within the Table of Contents.
\renewenvironment{abstract}{{\hspace{-2.2em} \huge \textbf{\abstractname}} \par}{\pagebreak}
\addcontentsline{toc}{chapter}{\hspace{-1.5em} ABSTRACT}
\begin{abstract}
\vspace{0.55ex}
\doublespacing
Insert the text of your abstract here.  Make sure there is one blank line between the end of the Abstract text and the ``end'' command below to maintain double--spaced lines.

\end{abstract}

\pagenumbering{arabic}
\addtocontents{toc}{\vspace{12pt} \hspace{-1.8em} CHAPTER \vspace{-1em}}
\singlespacing
\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
\setlength{\intextsep}{6pt plus 2pt minus 2pt}
\chapter{Introduction}
\doublespacing
\input{chapter1}
\pagebreak
\singlespacing
\chapter{A simple numerical solution for a PDE using the Discontinuous Galerkin method}
\doublespacing
\input{chapter2}
\pagebreak
\singlespacing
\chapter{A scalar field on a Schwarzschild background without a source}
\doublespacing
\input{chapter3}
\pagebreak
\singlespacing
\chapter{Circular orbits on a Schwarzschild spacetime}
\doublespacing
\input{chapter4}
\pagebreak
\singlespacing
\chapter{Elliptical orbits on a Schwarzschild spacetime}
\doublespacing
\input{chapter5}
\pagebreak
\singlespacing
\chapter{Extrapolating the self force to infinite Disctontinuous Galerkin order}
\doublespacing
\input{chapter6}
\pagebreak
\singlespacing
\chapter{Extrapolating the mode-summed self-force to include contributions from an infinite number of spherical harmonic modes}
\doublespacing
\input{chapter7}
\pagebreak
\singlespacing
\chapter{Future work: generic orbits via the osculating orbits framework}
\doublespacing
\input{chapter8}
\pagebreak
\singlespacing
%To insert additional chapters, copy the previous five lines, using chapterX as the argument of the 
%\input command for Chapter X, where X=6,7,8,...
\addtocontents{toc}{\vspace{12pt}}
\addcontentsline{toc}{chapter}{\hspace{-1.6em} REFERENCES}
\begin{thebibliography}{999}
\vspace{0.9em}
\input{bibliography}
\end{thebibliography}
%\pagebreak
%\singlespacing
%\addtocontents{toc}{\vspace{12pt} \hspace{-1.8em} APPENDIX \vspace{-1em}}
%\appendix
%\chapter{Title of Appendix A}
%\vspace{0.5em}
%\input{appendixA}
%\pagebreak
%\chapter{Title of Appendix B}
%\vspace{0.5em}
%\input{appendixB}
%\pagebreak
%If you need to insert additional appendices, copy the previous four lines, using appendixY as the
%argument of the \input commnd for Appendix Y, for Y=C,D,E,...

%Finally, the vita section is created and included in the Table of Contents.
\chapter*{Vita}
\doublespacing
\setlength{\parindent}{1.75em}
\vspace{0.2em}
\addtocontents{toc}{\vspace{12pt}}
\addcontentsline{toc}{chapter}{\hspace{-1.5em} VITA}
I have been interested in astronomy since I heard an audio book on planets as a four year old, before I could even read. In junior high and high school I was a serious math team competitor for the state of Minnesota. As a high school student I took extension courses through Northwestern University in modern physics and in C programming. Both of these courses were influential to me, but the modern physics course began my interest in general relativity. I also took most of a college math major (which I never completed) through University of Minnesota as a high school student. My first research experience in astronomy was as a high school student at Saint Cloud State University with Professor Maria Womack imaging comets and reducing data in IRAF. In my senior year, I was selected for the Physics Olympiad national training camp in 2000, and saw a presentation on the relatively newly discovered dark energy. I decided I wanted to go into cosmology.

In college I majored in physics and took electives in cosmology and art. I had research opportunities analyzing X-ray data from RXTE for Walter Lewin at MIT and simulating track reconstruction in the MINOS neutrino detector for Dr. Jeffrey Nelson and Professor Kenneth Heller at University of Minnesota.  The MINOS far detector was awe inspiring in both scale and complexity of cabling of the electronics structure. My undergraduate thesis involved the simulation of a strong gravitational lens survey, to determine whether it would be possible to use Einstein ring radii to measure cosmological parameters. Professor Jacqueline Hewitt was my thesis supervisor.

I chose to go to graduate school at The Ohio State University in astronomy, because I liked the research-focussed structure of the program. I had a University Fellowship for the first year, which was a nice bonus. I worked on a simulation of the stellar population along two galactic lines of sight to determine the frequency of transiting exoplanets with Professor Andrew Gould. I helped write an early draft of the publication that resulted. Ohio State proved to be a good choice, and I am very happy with the astronomy background I gained there; however, I found that I became more interested in particle astrophysics and the fundamental physics behind astronomy. We decided that I needed to make the transfer to a physics program. Professor John Beacom was willing to help me make this transfer to the Ohio State physics department, and that would have been an excellent choice; however, I wanted to marry my fiance, Chuck Hardin. After I obtained my Masters of Science in Astronomy from Ohio State, we moved to Minneapolis, where he was more able to get a job.

At the University of Minnesota, I worked toward a PhD in physics. Again, I was lucky enough to have a University Fellowship for the first year. I put it toward classes. At U of MN, most of my coursework was in particle physics. After the first year, I began to work on the NOvA neutrino oscillation experiment, the successor to MINOS, again under Professor Kennith Heller. This time I was working more directly as an instrumentalist, and I was bad at it. I passed both my qualifying exam and general exam (in neutrinos), but the experiment was nationally defunded and I wasn't given the option to TA. I found a new summer position in theoretical particle physics for Professor Arkady Vainshtein. There was no funding for it, though, and a better opportunity came along. I had the opportunity to work on LIGO! I joined Professor Vuk Mandic's research group. I retook and eventually passed my general exam, this time in cosmology.

For two and a half years, I worked with Professor Vuk Mandic, Dr. Eric Thrane, Dr. Jan Harms, and Shivaraj Kandhassamy on the STAMP gravitational wave transient search and on gravity gradient noise calculations and simulations for a third generation detector. I also did a small amount of data analysis of seismic waves from Homestake Mine, to evaluate it as a potential site for a third generation detector. I was involved in three published papers and one preprint, though I am an author on twenty-something papers due to LIGO collaboration publication rules. I had some chronic health problems, which eventually flared up into severe health problems. I was unable to obtain a medical leave. In the mean time, the Big Dog event happened. Professor Mandic and I were unable to find a mutually agreeable accommodation by which I could continue to work on the project at a lower level of urgency. I lost my funding and my advisor. I was unable to find another advisor, since I was already in my fifth year. Two years later, I got my Masters in Science in Physics from University of Minnesota.

In the mean time, I took classes at Saint Cloud State University as a non-degree student, and did research with Professor Gary Bohannan on fractional order integrators and differentiators, which are circuit devices that have Laplace transforms with fractional exponents in the denominator. I wrote the paper that resulted and submitted it for publication, but misunderstood the deadline and missed it. Unsurprisingly, it was not published. During this time I was also an amature astronomer, with limited but enthousiastic success.

Now I am a fourth year graduate student at Louisiana State University, exactly where I intended to be. My coworkers are good friends. I got to perform photometry of exoplanets with a telescope and analyze the data for myself, bringing a previous project full circle. I have worked on LIGO during the time of three detections. I have had the opportunity to begin to learnmultiple techniques for speeding up code and measuring that speed up on supercomputers. I have done a little work with databases and and more with numerical algorithms, and learned a couple of new programming languages. I have had the opportunity to continue to contribute to the field of general relativity and participate in a department where my broad background in the connections between various fields of astronomy is valued. I have helped supervise undergraduate research progress, guided a junior high student through a science fair poject, judged four undergraduate research poster sessions, helped coordinate a science summer camp, and made a lesson plan for and taught a graduate class once. This document contains the research I have produced in the last three years since I arrived on June 3, 2014 at LSU and began working with Peter Diener. These have been the best three years of my life.

When interpreting the name on this document, please understand that I am female to male transgendered and that my legal name is Susan Elaine Dorsher but that I go by Steven James Dorsher. I am legally female, use male pronouns, and think of myself as something in the middle.
\end{document}





